The SWF Model simulates one-dimension routing of surface water using the Muskingum routing approach.

\subsection{Units of Length and Time}
The SWF Model simulates surface water routing without using prescribed length and time units. Any consistent units of length and time can be used when specifying the input data for a simulation. This capability gives a certain amount of freedom to the user, but care must be exercised to avoid mixing units.  The program cannot detect the use of inconsistent units.

\subsection{Flow Budget}
A summary of all inflow (sources) and outflow (sinks) is called a flow budget.  \mf calculates a flow budget for the overall model as a check on the acceptability of the solution, and to provide a summary of the sources and sinks to the flow system.  The flow budget is printed to theSWF Model Listing File for selected time steps.

\subsection{Time Stepping}

For the present implementation of the SWF Model, all terms in the routing equation are solved explicitly.  In \mf time step lengths are controlled by the user and specified in the Temporal Discretization (TDIS) input file.  Instructions for specifying time steps are described in the TDIS section of this user guide.  

\newpage
\subsection{SWF Model Name File}
\input{swf/namefile.tex}

\newpage
\subsection{Line Network Discretization (DISL) Package}
\input{swf/disl}

\newpage
\subsection{Muskingum Routing (MMR) Package}
\input{swf/mmr}

\newpage
\subsection{Muskingum-Cunge-Todini (MCT) Package}
\input{swf/mct}

\newpage
\subsection{Cross Section (CXS) Package}
\input{swf/cxs}

%\newpage
%\subsection{Initial Conditions (IC) Package}
%\input{swf/ic}

\newpage
\subsection{Output Control (OC) Option}
\input{swf/oc}

%\newpage
%\subsection{Observation (OBS) Utility for a GWT Model}
%\input{swf/swf-obs}

\newpage
\subsection{Inflow (FLW) Package}
\input{swf/flw}


